Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-11 journal paper/content/related_work.tex
Slightly reworded the last para.

Finally, relaxed versions of rationality similar to ours are found in several notable lines of work. For example, ``random agents" (a.k.a. noise traders) can side-step the ``no-trade theorem'' \citep{Milgrom-Stokey-82}, a famous impossibility result in financial economics. The \SoftMaxRandom model is closely related to the literature on \emph{product differentiation}, starting from \cite{Hotelling-29}, see \cite{Perloff-Salop-85} for a notable later paper. There is a large literature on non-existence of equilibria due to small deviations   (which is related to the corresponding result for \HardMaxRandom), starting with \cite{Rothschild-Stiglitz-76} in the context of health insurance markets. Notable recent papers \citep{Veiga-Weyl-16,Azevedo-Gottlieb-17} emphasize the distinction between \HardMax and versions of \SoftMaxRandom. \gaedit{We utilize first-mover advantage and relaxed versions of rationality to model varying competition, instead of classic market ``competitiveness" measures such as the Lerner Index or the Herfindahl-Hirschman Index, since these measures rely on ex-post observable attributes of a market such as prices or market shares \cite{tirole1988theory}. However, neither is applicable to our setting: in our model, there are no prices, and market shares are endogenous.}

\ascomment{Guy: In EC20 you cited \cite{kerin1992first} for a survey on first-mover advantage. Why not now? Likewise, you also had a para on Lerner Inder and such (last para in related work in EC20).}
\gacomment{Good catch, I re-added them back in. I had removed \cite{kerin1992first} since I added more directly relevant papers to the first-mover advantages in our model.}

>>>>

Relaxed versions of rationality similar to ours are found in several notable lines of work. For example, ``random agents" (a.k.a. noise traders) can side-step the ``no-trade theorem'' \citep{Milgrom-Stokey-82}, a famous impossibility result in financial economics. The \SoftMaxRandom model is closely related to the literature on \emph{product differentiation}, starting from \cite{Hotelling-29}, see \cite{Perloff-Salop-85} for a notable later paper. There is a large literature on non-existence of equilibria due to small deviations   (which is related to the corresponding result for \HardMaxRandom), starting with \cite{Rothschild-Stiglitz-76} in the context of health insurance markets. Notable recent papers \citep{Veiga-Weyl-16,Azevedo-Gottlieb-17} emphasize the distinction between \HardMax and versions of \SoftMaxRandom.

We use first-mover advantage and relaxed versions of rationality to model varying competition, instead of classic ``market competitiveness" measures such as the Lerner Index or the Herfindahl-Hirschman Index
\citep{tirole1988theory}. The latter measures rely on ex-post observable attributes of a market such as prices or market shares. Neither is applicable to our setting, since there are no prices, and market shares are endogenous.

\ascomment{Guy: slightly reworded the previous para.}
